### 2015-05-22 writing/SNLI paper/corpus.tex
Misc, including rc3 stats.

The instructions that we provided to the workers are shown in Fig.~\ref{instructions-1}. Below the instructions were three fields for each of three requested sentences, corresponding to our \ii{entailment}, \ii{neutral}, and \ii{contradiction} labels, a fourth field (marked optional) for reporting problems, and a link to an FAQ page. That FAQ grew over the course of data collection, but discussed disallowed techniques (e.g., reusing the same sentence for many different prompts, which we saw in a few cases), sentence length and complexity (we did not enforce a minimum length, and we allowed bare NPs as well as full sentences), and logistical issues around payment timing.

@@

\todo{Do we need statistics about the number/distribution of workers?}

@@

This validation phase is not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ.

@@

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{7.5cm}lp{5.5cm}}
  \toprule
A young man in a striped hoodie looks at an artistic Levi's advertisement that says "We are all workers." & \ii{entailment} & There is a man in a hoodie looking at an advertisement.\\
\rule{0pt}{3ex}Two men on laptops in a dark room. & \ii{entailment} & Two men are on their laptops.\\
\rule{0pt}{3ex}A naked baby and toddler smear each other in paint. & \ii{neutral} & The kids are in the bathtub.\\
\rule{0pt}{3ex}A woman is focusing on her game of curling. & \ii{neutral} & There is a women playing a game indoors\\
\rule{0pt}{3ex}A group of people dressed in green and white are dancing in a circle outside of a white building. & \ii{contradiction} & A group performs indoors.\\
\rule{0pt}{3ex}A balding professor giving a lecture to students on the topic of "opportunity". & \ii{neutral} & A female professor with hair giving a lecture to students.\\
    \bottomrule
% From 1.0rc2`
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from SNLI.\\
\todo{Replace with *validated* examples from the post-rc2 training set, include all 5 labels.}}
\end{table*}

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Training pairs &  550,159\\
Development pairs &  9,999\\
Test pairs &  9,999\\
\textbf{Total sentence pairs} & 570,157\\
\midrule
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
Premise complete sentences & 70.2 ??\%\\
Hypothesis complete sentences & 75.4 ??\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc2
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs & 53,852\\
gold label $\ne$ original label & 8.5\%\\
Unanimous gold & 57.7\%\\
No gold (no 3 labels match) & 2.1\%\\
Label $=$ gold & 88.9\%\\
Label $=$ original author's label & 85.5\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc2
\caption{\label{validation-stats}Key statistics for the validated sentence pairs.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &33.3 & 33.4 & 33.3 \\
\ii{neutral} & 33.2 & 33.2 & 33.2 \\
\ii{contradiction} & 33.3 & 33.2 & 33.3 \\
- (no consensus) & 0.2 & 0.2 & 0.2 \\
\bottomrule
  \end{tabular}
  % From 1.0rc2
\caption{\label{validation-freq}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}

>>>>

The instructions that we provided to the workers are shown in Fig.~\ref{instructions-1}. Below the instructions were three fields for each of three requested sentences, corresponding to our \ii{entailment}, \ii{neutral}, and \ii{contradiction} labels, a fourth field (marked optional) for reporting problems, and a link to an FAQ page. That FAQ grew over the course of data collection, but discussed disallowed techniques (e.g., reusing the same sentence for many different prompts, which we saw in a few cases), sentence length and complexity (we did not enforce a minimum length, and we allowed bare NPs as well as full sentences), and logistical issues around payment timing. About 2500 workers contributed data.

@@

@@

This validation phase is not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.

@@

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{7.5cm}lp{5.5cm}}
  \toprule
A young man in a striped hoodie looks at an artistic Levi's advertisement that says "We are all workers." & \ii{entailment} & There is a man in a hoodie looking at an advertisement.\\
\rule{0pt}{3ex}Two men on laptops in a dark room. & \ii{entailment} & Two men are on their laptops.\\
\rule{0pt}{3ex}A naked baby and toddler smear each other in paint. & \ii{neutral} & The kids are in the bathtub.\\
\rule{0pt}{3ex}A woman is focusing on her game of curling. & \ii{neutral} & There is a women playing a game indoors\\
\rule{0pt}{3ex}A group of people dressed in green and white are dancing in a circle outside of a white building. & \ii{contradiction} & A group performs indoors.\\
\rule{0pt}{3ex}A balding professor giving a lecture to students on the topic of "opportunity". & \ii{neutral} & A female professor with hair giving a lecture to students.\\
    \bottomrule
% From 1.0rc2
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from SNLI.\\
\todo{Replace with *validated* examples from the post-rc2 training set, include all 5 labels.}}
\end{table*}

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Training pairs &  550,153\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs & 59,445\\
gold label $\ne$ original label & 8.4\%\\
Unanimous gold & 58.2\%\\
No gold (no 3 labels match) & 1.9\%\\
Label $=$ gold & 89.0\%\\
Label $=$ original author's label & 85.7\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc3
\caption{\label{validation-stats}Key statistics for the validated sentence pairs.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &33.3 & 33.3 & 33.7 \\
\ii{neutral} & 33.2 & 32.4 & 32.2 \\
\ii{contradiction} &  33.3 & 32.7 & 32.4  \\
- (no consensus) & 0.1 & 1.6 & 1.8 \\
\bottomrule
  \end{tabular}	
% From 1.0rc3
\caption{\label{validation-freq}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}
